Capstone Movielens Report

### 2025-12-24 reports/capstone-movielens.site/02.5.UME-model.Rmd
Fix for report section review: Movie Effect Analysis.

Now, we can figure out the most given ratings in order from most to least. The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L422) below performs this operation:
```{r  main-script@l422, eval=FALSE}
edx.rating_groups <- edx |>  group_by(rating) |>
     summarise(count = n()) |>
     arrange(desc(count))
```
```{r, include=TRUE}
edx.rating_groups
```

@@

The following code allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
```{r, include=TRUE}
edx.rating_groups |> arrange(rating)
```

We can visualize this using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L433) to plot the data:
```{r  main-script@l433}
edx.rating_groups |>
  ggplot(aes(x = rating, y = count)) +
  geom_line()

```

>>>>

Now, we can figure out the most given ratings in order from most to least. The [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L422) below performs this operation:
```{r  main-script@l422, eval=FALSE}
edx.rating_groups <- edx |>  group_by(rating) |>
     summarise(count = n()) |>
     arrange(desc(count))
```
```{r}
print(edx.rating_groups)
```

@@

The following [line of code](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L430) allows us to summarize that in general, half-star ratings are less common than whole-star ratings (e.g., there are fewer ratings of 3.5 than there are ratings of 3 or 4, etc.):
```{r  main-script@l430, include=TRUE}
print(edx |> group_by(rating) |> summarize(count = n()))
```

We can give even more visibility for the *rating distribution* by plotting the data for the *rating groups* (the `edx.rating_groups` object) we obtained above using the following [code snippet](https://github.com/AzKurban-edX-DS/Capstone-MovieLens/blob/main/r/src/capstone-movielens.main.R#L433):

```{r  main-script@l433}
edx.rating_groups |>
  ggplot(aes(x = rating, y = count)) +
  geom_line() 
```
